---
title: "SimpleRegress"
author: "Jonathan Campos"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
bAGE <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(bAGE)
summary.lm(bAGE)
```
we want to compare the neck with age to the other model with neck.Ordering by adjusted R square in the model with neck we got 0.7476 and for the age model it was 0.5073. With this we found out that neck is better than age 


```{r}
bHEADLEN <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(bHEADLEN)
summary.lm(bHEADLEN)
```
after comparing the neck model, the AGE, NECK, and the HEADLEN in order form biggest to smallest is HEADLEN -0.8434, NECK -0.7476, and AGE -0.5073 

```{r}
bHEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(bHEADWTH)
summary.lm(bHEADWTH)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

